Automated Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-03-10 paper.tex
corrections to the new text

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as:
%
\begin{enumerate}
	\item Time and energy constraints;
	\item Handling of concurrent software;
	\item Platform restrictions;
	\item Verification of code pieces or modules that rely on larger structures;
	\item Legacy designs; %, which are usually developed with low-level languages.
	\item Support to different programming languages, frameworks, and interfaces;
	\item Correct code instrumentation;
	\item Handling of non-linear and non-convex optimization problems;
	\item Incorporation of new and adapted checks, due to system or environment change;
	\item \textcolor{blue}{Provide a form of system evolution, in such a way that a version more adapted to the current scenario is obtained.}
\end{enumerate}

@@

\textcolor{blue}{The tenth aspect is related to the current development and test strategies adopted for embedded systems, which aim at simply providing robust structures, instead of antifragile ones. In summary, it is not feasible to account for every scenario or error, but it would be more interesting to provide a module or structure capable of thriving on problems and getting more robust. Such an aspect shares some similarity with the ninth one and may also be achieved through ML techniques.}

@@

\textcolor{blue}{Due to the fact that the mentioned research problems are the focus of the present technology area, many works tackled them and other researchers still address them. As a consequence, we can cite the followinf contributions toward them.}

@@

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et al.} \cite{amoedo} proposed a modulation classification methodology, with the goal of spectrum sensing for opportunistic transmissions. Besides a correct software implementation, {\it i.e.}, source code, which is already covered by formal methods already available in literature \cite{esbmc_filter,Cordeiro12,Clarke04}, one may argue if the proposed methodology is able to recognize modulations under some reception condition, such as severe analog interference. This way, it would be interesting to develop a verification module for transmission and reception software, which could be capable of creating inputs related to sampled radio frequency signals, under a variety of conditions, and then unifying source code and behavior verification. In addition, that kind of implementation usually employs digital filters with specific parameters, which could also be tackled. Indeed, communication aspects of ECPSs could be tackled, as a module in system verification procedures.

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying the desired constraints. Bridge studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Seshia {\it et al.}~\cite{Seshia17}, in turn, showed that control syntheses based on ML is also a trend, since it has been applied to different applications and model classes~\cite{Jha10,Sadigh14}. Finally, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms. As a consequence of what was presented, it seems worthwhile to pursue integration of ML into BMC-based checkers, given that it has the potential to tackle many open problems or at least enhance existing solutions.

\textcolor{blue}{In addition, a aspect closely related to ML techiniques, as mentioned in Section \cite{Verification-Challenges}, is system fragility. Currently, most design strategies try to produce robust systems, which are able to deal with a limited set of common errors that happen when they are operating, {\it i.e., they are robust}. Nonetheless, that is effective only if problems foreseen during design phases happen; otherwise, operation may be compromised.}

@@

\textcolor{blue}{As a result, it may be more interesting to develop methodologies that are not simply robust, regarding a predetermined condition, but instead thrive on problems and grow stronger (as the human body, which gets stronger when exposed to germs), which leads to antifragile systems. In engineering, we are only beginning to develop solutions that can be classified as antifragile, such as multiple-input/multiple-output (MIMO) systems, which use multiple signal copies together with multipath to achieve performance enhancement~\cite{spectrum2013}.}

\textcolor{blue}{Systems that could greatly benefit from being antifragile are the cyber-physical ones, which interact with other external systems and use their internal representations to interpret physical properties. As faults occur, which may be treated with some sort of system elasticity, and external environments are normally dynamic, given that it naturally changes with time, variations in operating conditions happen and should be tolerated, in order to keep behavior quality \cite{antifragile}. Besides, when discussing the fundamentals of antifragility, it is difficult not to tackle machine learning \cite{antifragile}, which has the potential to provide some wisdom regarding correct behavior and internal representations, in order to keep a system working in a volatile environment.}

\textcolor{blue}{For instance, we could think about a system including an adaptation module composed by two elements: a machine learning engine, capable of capturing current behaviors and identify different trens, and a SMT-based verification method, capable of recursively performing retuning procedures, which could test new parameters suggested by the machine learning module and then judge theis suitability. As a consequence, we would be able to design systems with the potential to being antifragile, given that they would learn from new challenges and then modify its behavior model, in order to account for new errors and threats.}

>>>>

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allows specific checks regarding system behavior and not only code correctness. Additionally, embedded-system verification raises additional challenges, such as:
%
\begin{enumerate}
	\item Time and energy constraints;
	\item Handling of concurrent software;
	\item Platform restrictions;
	\item Verification of code pieces or modules that rely on larger structures;
	\item Legacy designs; %, which are usually developed with low-level languages.
	\item Support to different programming languages, frameworks, and interfaces;
	\item Correct code instrumentation;
	\item Handling of non-linear and non-convex optimization problems;
	\item Incorporation of new and adapted checks, due to system or environment change;
	\item \textcolor{blue}{Provision of a form of system evolution, in such a way that a version more adapted to a given scenario is obtained.}
\end{enumerate}

@@

\textcolor{blue}{The tenth aspect is related to the current development and test strategies adopted for embedded systems, which aim at simply providing robust structures, instead of antifragile ones \cite{antifragile}. In summary, it is not feasible to account for every error or faulty scenario and then it would be more beneficial to provide a module, architecture, or methodology capable of thriving on problems and getting stronger. Such an aspect shares some similarity with the ninth one and may also be achieved through ML techniques. Indeed, this kind of scheme consists in a completely different approach, which would profoundly change the way we design embedded systems.}

@@

\textcolor{blue}{Due to the fact that the mentioned research problems are the some of the main issues found in the technology area addressed in this article, many works tackled them and other researchers still perform experiments and suggest new methodologies and schemes for mitigating or solving their consequences. As a result, we can cite the following contributions toward them, which already provide some answers or at least present promissing approaches.}

@@

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et al.} \cite{amoedo} proposed a modulation classification methodology, with the goal of spectrum sensing for opportunistic transmissions. Besides a correct software implementation, {\it i.e.}, correct source code, which is already covered by formal methods already available in literature \cite{esbmc_filter,Cordeiro12,Clarke04}, one may argue if the proposed methodology is able to recognize modulations under some reception condition, such as severe analog interference. This way, it would be interesting to develop a verification module for transmission and reception software, which could be capable of creating inputs related to sampled radio frequency signals, under a variety of conditions, and then unifying source code and behavior verification. In addition, that kind of implementation usually employs digital filters with specific parameters, which could also be addressed. Indeed, communication aspects of ECPSs could be tackled, as properties in system verification procedures.

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying desired constraints. Bridge, Holden, and Paulson \cite{} studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Seshia {\it et al.}~\cite{Seshia17}, in turn, showed that control syntheses based on ML is also a trend, since it has been applied to different applications and model classes~\cite{Jha10,Sadigh14}. Finally, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms. As a consequence of what was presented, it seems worthwhile to pursue integration of ML into BMC-based checkers, given that it has the potential to tackle many open problems or at least enhance existing solutions.

\textcolor{blue}{In addition, another aspect closely related to ML techniques, as mentioned in Section \ref{Verification-Challenges}, is system fragility. Currently, most design strategies try to produce robust systems, which are able to deal with a number of errors that happen when they are operating. Nonetheless, that is effective only if problems foreseen during design phases happen; otherwise, operation may be severely compromised and even cause loss of lives.}

@@

\textcolor{blue}{As a result, it may be more interesting to develop methodologies that are not simply robust, regarding predetermined conditions, but instead thrive on problems and grow stronger (as the human body, which gets stronger when exposed to germs), which leads to antifragile systems. In engineering, we are only beginning to develop solutions that can be classified as antifragile, such as multiple-input/multiple-output (MIMO) systems, which use multiple signal copies together with multipath to achieve performance enhancement~\cite{spectrum2013}. In that case, signal copies would initially result in a destructive effect; however, with the use of a methodology that takes advantage on them, the net result is performance improvement.}

\textcolor{blue}{Systems that could greatly benefit from being antifragile are the cyber-physical ones, which interact with other external elements and use their internal representations to interpret physical properties. As faults occur, which may be treated with some sort of system elasticity, and external environments are normally dynamic, given that it naturally changes with time, variations in operating conditions happen and should be tolerated, in order to keep behavior quality \cite{antifragile}. Besides, when discussing the fundamentals of antifragility, it is difficult not to tackle machine learning \cite{antifragile}, which has the potential to provide some wisdom regarding correct behavior and internal representations, in order to keep a system working in a volatile environment.}

\textcolor{blue}{For instance, we could think of a system including an antifragility module composed by two elements: a machine learning engine, capable of capturing current behaviors and identifying different trends, and a SMT-based verification method, capable of recursively performing retuning procedures, which could test new parameters estimated from the data provided by the machine learning module and then test new behaviors based on them, through counterexamples. In addition, there could also be a measurement module, which would also judge some metrics regarding the new behavior ({e.g.}, signal-to-noise-error). As a consequence, we would be able to design systems with the potential of being antifragile, given that they would learn from new challenges and then modify its behavior model, in order to account for new errors and threats and even benefit from them.}
